IDEA:
Women has short trip duration of usage of citibike than men.

NULL HYPOTHESIS:

The women's trip duration that use of citi-bike is the same or higher than the men's trip duration of usage of the bike.

\section{$H_0$ : $\frac{F_{Wd}}{W_{n}} >= \frac{F_{Md}}{M_{n}} $ }



\section{$H_1$ : $\frac{F_{Wd}}{W_{n}} < \frac{F_{Md}}{M_{n}} $}

where $F_{Wd}$ is Frequency of Women trip duration, $F_{Md}$ is Frequency of Men trip duration, ${W_{n}}$ is total number of Women, and ${M_{m}}$ is total number of Men

or identically:

$H_0$ : $\frac{F_{Wd}}{W_{n}} - \frac{F_{Md}}{M_{n}} $ >= 0

$H_1$ : $\frac{F_{Wd}}{W_{n}} - \frac{F_{Md}}{M_{n}} $ < 0

\subsection{The significance level is chosen to $\alpha=0.05$}

\subsection{which means i want the probability of getting a result at least as significant as mine to be less then 5 \%}


The citi-bike is a bike sharing system that is run by Motivate according to Citi-Bike homepage\cite{nyc}. The system

"Citi Bike is New York City’s bike share system, and the largest in the nation. Citi Bike launched in May 2013 and has become an essential part of our transportation network. It's fun, efficient and affordable – not to mention healthy and good for the environment.
Citi Bike, like other bike share systems, consists of a fleet of specially designed, sturdy and durable bikes that are locked into a network of docking stations throughout the city. The bikes can be unlocked from one station and returned to any other station in the system, making them ideal for one-way trips. People use bike share to commute to work or school, run errands, get to appointments or social engagements, and more.
Citi Bike is available for use 24 hours/day, 7 days/week, 365 days/year, and riders have access to thousands of bikes at hundreds of stations across Manhattan, Brooklyn, Queens and Jersey City." 